Contention Management for 5G

### 2017-02-01 article/article.tex
algo ecrit

   \subsection{Problems}

@@

@@

  \subsection{No waiting times}
    \subsubsection{Shortest-longest}
      \paragraph{Algo}
      \paragraph{Period}
    \subsubsection{Exhaustive generation}
      Décrire l'algo, expliquer les coupes
    \subsubsection{Results}
      Resultats des simulations : Shortest-longest optimal pour ces parametres.

>>>>

      \begin{center}

      \fbox{\parbox{12cm}{
      Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
      Indeed, consider messages of size 1, we can build a graph, with $c$ routes $r_i \in {\cal R}_{\cal C}, i < c$ which all intersect two by two and
      such that if $r_i$ and $r_j$ have $v$ as first common vertex we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.
      Therefore there is a $2$-periodic affectation by setting all $m_i$ to $0$.

      A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$. The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.

      Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$. The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.

      A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.

      \begin{tabular}{cc}
      \includegraphics[scale=0.5]{Fig5.pdf} & \includegraphics[scale=1]{Fig7.pdf}\\
      $\lambda(v,r_i) - \lambda(v,r_j)=1$ & Conflict graph\\
      \end{tabular}\newline

      On the other hand if we set all $\lambda(v,r_i) - \lambda(v,r_j)=P$, there is no $P$-periodic affectation if $P<l$.

      \begin{tabular}{cc}
      \includegraphics[scale=0.5]{Fig6.pdf} & \includegraphics[scale=1]{Fig8.pdf}\\
      $\lambda(v,r_i) - \lambda(v,r_j)=2$ & Conflict graph\\
      \end{tabular}\newline
      \begin{center}
      Here for P=2, there is no $P$-periodic affectation.
      \end{center}

      Therefore if we choose and odd value for $P$ and $l=P+1$, there is no $P$-periodic affectation but modulo $2$ all $\lambda(v,r_i) - \lambda(v,r_j)$
      are equal to one thus we have a $2$-periodic affectation. 
      }}

      \end{center}
   \subsection{Problems}

@@

    \scalebox{0.5}{

    \begin{tikzpicture}

    \tikzset{
      LabelStyle/.style = { rectangle, rounded corners, draw,
			  font = \bfseries },
      EdgeStyle/.append style = {->} }
      \SetGraphUnit{5}
      \Vertex[x=4,y=2]{s3}
      \Vertex[x=0,y=4]{s2}
      \Vertex[x=0,y=6]{s1}

      \Vertex[x=12,y=3]{l3}
      \Vertex[x=14,y=4]{l2}
      \Vertex[x=10,y=2]{l1}
      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
	\tikzset{
      VertexStyle/.append style = {blue} }
	\Vertex[x=-8,y=3]{1}
	      \tikzset{
      VertexStyle/.append style = {green} }
	  \Vertex[x=-7,y=5]{2}

	    \tikzset{
      VertexStyle/.append style = {red} }
	  \Vertex[x=-6,y=4]{3}
		\tikzset{
      VertexStyle/.append style = {black} }

      \SetVertexNoLabel
      \Vertex[x=2,y=5]{A}
      \Vertex[x=4,y=5]{B}
      \Vertex[x=10,y=5]{C}
      \Vertex[x=12,y=5]{D}
      \Vertex[x=6,y=3]{E}
      \Vertex[x=8,y=3]{F}
      \tikzset{
      EdgeStyle/.append style = {green} }
      \Edge[label = 3](s2)(A)
      \Edge(A)(B)
      \Edge(B)(C)
      \Edge(C)(D)
      \Edge(D)(l2)

      \tikzset{
      EdgeStyle/.append style = {red} }
      \Edge[label = 1](s3)(E)
      \Edge(E)(F)
      \Edge(F)(l3) 
	\tikzset{
      EdgeStyle/.append style = {blue} }
      \Edge[label = 1](s1)(A)
      \Edge[label = 1](A)(B)
      \Edge[label = 1](B)(E)
      \Edge(E)(F)
      \Edge(F)(l1)

	\tikzset{
      EdgeStyle/.append style = {black,-} }

      \Edge(1)(2)
      \Edge(1)(3)
    \node (1) at (-3,4){\Huge $\rightarrow$};
    \end{tikzpicture}

    }\\

@@

  \subsection{No waiting times}
    \subsubsection{Shortest-longest}
      \paragraph{Algo}
      \paragraph{Period}
    \subsubsection{Greedy Algorithm with higher bound}

	\begin{algorithm}[H]
	\caption{Greedy with Higher bound Period(GHP)}
	\begin{algorithmic}
	\REQUIRE ${\cal R}_{\cal C}$, period $P$
	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
	\STATE $P1[P]$ slots of size $\tau$ in first way period.
	\STATE $P2[P]$ slots  of size $\tau$ in back way period.
	\FORALL{route i in ${\cal R}_{\cal C}$ }

	\FORALL{slot j in P1}

	\IF{$P1[j]$ is free, and the corresponding slot(s) in P2 are free}

	\STATE $o_i \leftarrow j$
	\ENDIF

	\IF{No intervals are found for i}
	\STATE return FAILURE
	\ENDIF
	\ENDFOR

	\ENDFOR

	\end{algorithmic}
	\end{algorithm}
      \paragraph{Period}
	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots. Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way. Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
	\todo{Dessin qui illustre ça}\\
	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period. Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period. Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.

    \subsubsection{Exhaustive generation}
      Décrire l'algo, expliquer les coupes
    \subsubsection{Results}
      Resultats des simulations : Shortest-longest optimal pour ces parametres.
